---
title: "Plotting"
author: "| Rodrigo Esteves de Lima-Lopes \n| University of Campinas \n| rll307@unicamp.br\n"
output: 
  md_document:
    variant: markdown_github
  html_document:
    toc: yes
  pdf_document:
    toc: yes
    number_sections: yes
---
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This script was developed for the analysis of Portuguese. I hope it helps colleagues in the LC area and popularize the use of R. It is part of our research project developed with CNPQ. Please drop me a line if you have any doubts or need any help.

# Purpose of this repository

This git brings the scripts for my article:

- Lima-Lopes R.E. (forthcoming). Beyond the Binary: Trans Women's Video Activism on YouTube. Accepted for publication at *Digital Scholarship in the Humanities*. 

This script is specifically about **plotting**.



# Packages

For data processing we are going to need some packages:


```{r packages, eval=FALSE}
library(dbplyr)
library(ggplot)
library(ggridges)
```

# Plotting

Definig the color and ploting graph 1

```{r graph1, eval=FALSE}
colour <-"bisque4"
df_topics  %>% 
  count(topic) %>% 
  mutate(topic = forcats::fct_reorder(topic, n)) %>% 
  ggplot(aes(x = topic, y = n)) + 
  geom_col(fill = colour) +
  theme_minimal() + 
  labs(x = "Topics", y = "Videos",
       title = NULL) +
  coord_flip()
```


Definig the color and ploting graph 2

```{r graph2, eval=FALSE}
df_topics$channel <-as.factor(df_topics$channel)
df_topics$topic <- as.factor(df_topics$topic)

xtabs(~ channel + topic, df_topics) %>% 
  as.data.frame() %>% 
  ggplot(aes(channel, topic)) + 
  geom_tile(aes(fill = Freq)) +
  scale_fill_gradient(low="#D6D2C4", high="#575257")+
  geom_text(aes(label = round(Freq, 1))) +
  labs(x = "Channels", y = "Topics",
       title = NULL)
```






















