---
title: "Concordancing"
author: "| Rodrigo Esteves de Lima-Lopes \n| University of Campinas \n| rll307@unicamp.br\n"
output: 
  md_document:
    variant: markdown_github
  html_document:
    toc: yes
  pdf_document:
    toc: yes
    number_sections: yes
---
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction

This script was developed for the analysis of Portuguese. I hope it helps colleagues in the LC area and popularize the use of R. It is part of our research project developed with CNPQ. Please drop me a line if you have any doubts or need any help.

# Purpose of this repository

This git brings the scripts for my article:

- Lima-Lopes R.E. (forthcoming). Beyond the Binary: Trans Women's Video Activism on YouTube. Accepted for publication at *Digital Scholarship in the Humanities*. 

This script is specifically about **Concordancing**.


# Package

For concordancing we will need only one package

```{r package, eval=FALSE}
library(quanteda)
```

Creating the corpus

```{r corpus, eval=FALSE}
corpus.caption <- corpus(df_topics, 
                     text_field = "caption", metacorpus = NULL, 
                     compress = FALSE)
```

Please, change the variable `pattern` for the word of your interest and `window` for the number of words (left and right)

```{r conc, eval=FALSE}

kwic(corpus.caption, pattern = "amiga", 
                  window =6, valuetype = "fix")

```



